\subsection*{Lazer Blast}\label{lazer-blast}

``Lazer Blast'' is an arcade style shooter (like
\href{https://en.wikipedia.org/wiki/Galaga}{Galaga}), which includes
aspects of color matching and pattern matching.

\subsubsection*{Running}\label{running}

To install and run the game, clone this repository and \texttt{cd} into
it in a terminal. Then, run:

\begin{verbatim}
python3 setup.py install
\end{verbatim}

You can then enter the command,

\begin{verbatim}
lazerblast
\end{verbatim}

And the game will start.

\subsubsection*{Game-play}\label{game-play}

The user pilots a small ship against hoards of enemies. Each enemy has a
given color. The player must use a similar-colored laser to destroy that
enemy. For example, an enemy which is green much be shot with a green
laser. A red laser will have no effect. Waves of enemies come in
patterns: an astute fighter will be able to predict the next wave from
the previous, and will have a significant advantage over the enemy.

Since the player cannot be expected to handle the copious masses of
colorful enemies immediately, the difficulty of the game increases as
the player progresses, starting with a single color and slowly adding
other colors and increasing the speed.

\subsubsection*{Development}\label{development}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Clone the repository.
\item
  Install the requirements and game:

\begin{verbatim}
pip install -r requirements.txt
python3 setup.py develop
\end{verbatim}

  \emph{NB.} In the future, the requirements should be handled by the
  setup file.
\item
  Run the game:

\begin{verbatim}
lazerblast
\end{verbatim}
\end{enumerate}

\emph{NB.} Using a \texttt{virtualenv} would be preferable, but it does
not work (at least, not on a mac.) See
\href{https://bitbucket.org/pygame/pygame/issues/203/window-does-not-get-focus-on-os-x-with}{this}

\subsubsection*{Running Tests}\label{running-tests}

Tests are run with the \texttt{pytest} runner through the setup utility:

\begin{verbatim}
python3 setup.py test
\end{verbatim}
