% (1)	First paragraph:
% Describe why you have chosen this research project/topic (your
% motivation for choosing this topic).
Arcade style shooters enjoyed popularity throughout the 1980s and 1990s.
Color and pattern matching games such as \textit{Simon}, \textit{Bop-It},
and \textit{Twister} were also popular during this time.  While the
popularity of both genres may have waned in recent years, the
purchasing power and free time of the children who grew up in these
decades has increased dramatically.  Few video games have tried to
capitalize on the combined potential of these genres.

% (2)	Second paragraph:
% Describe what you are going to do for your proposed project to make
% it different from the existing projects.
% Read the sample abstract and learn from it.
In this paper, we present a coherent schema for combining aspects of
pattern-matching and arcade style shooters from the late 1980s and
early 1990s.  Arcade replicas, and color matching games from this era
are plentiful, but most games which amalgamate the two concepts are based on
rhythm and music (e.g. \textit{Rock Band}, \textit{Frets on Fire}, etc.) We
further assess the balance of game difficulty necessary to maintain
user engagement.  We report qualitative results of players using a
purpose-built color matching arcade style shooters built in Python.
Research was completed using small focus groups.

% (3)	Third paragraph:
% Describe the result of your research project.
% Read the sample abstract and learn from it.
Our results demonstrate that an engaging arcade-style experience is possible
when combined with basic color matching. However, we present evidence
suggesting that the action in such a game must be well-balanced to avoid
becoming overly-difficult.
