% Chapter 7	Acceptance Criteria
The criteria for acceptance of the project will proceed in stages.
A prototype of Lazer Blast will first be produced.  For acceptance,
the following criteria must be met:

\begin{itemize}
    % Menu
    \item A new user can begin a new game after looking at the menu
          for less than 1 minute.
    \item A new user can quit the game after looking at the menu
          for less than 1 minute.

    % Gameplay
    \item The user can fire upon an enemy.
    \item The user can navigate around their environment.
\end{itemize}

Once the prototype has been accepted, the final acceptance criteria
will include all the previous criteria as well as the following:

\begin{itemize}
    % Menu
    \item There is a main menu with the following items:
    \begin{itemize}
        \item New Game
        \item Statistics
        \item Quit
    \end{itemize}
    \item A new user can read all items in the menu.
    \item The colors in the menu have the same theme as those of the game.

    % Gameplay
    \item Firing a dissimilar laser at an enemy does no damage.
    \item The weapon, when fired, reaches the enemy faster than they can move away.
    \item The keys for movement are all within one hand's distance, as are the
          keys for using weapons.
    \item A new user can tell the difference between the different laser colors. (That
          is, the contrast is high enough for the average player.)
    \item A new user can tell which laser color is necessary for a given enemy.
\end{itemize}
