% Chapter 6	Exception Handling

Exception handling
There are a number of exceptions that may occur and disrupt the experience of 
the user.

Collision detection errors
The users in-game character should be destroyed by colliding with in-game
enemies and laser beams. Should the game fail to detect collisions, the in-game
enemies or player may become invulnerable. Should the collision detection
produce false-positives, the user may lose the game without failing to dodge
enemies and laser beams.

Movement errors
The user's in-game character should remain on screen at all times. If the code
responsible for this task should fail, the user's session will be disrupted.

Audio exceptions
If a user's audio drivers are missing or corrupted, the game's sound will not
function properly. Most properly-installed operating systems should not
encounter this exception.

Frame-Rate Exceptions
The game should update at a constant rate of rendered frames per second. If the
code responsible fails, the game may perform at an accelerated pace on faster
computers, making the game far more difficult to play than on slower computers. 

Graphics Scaling exceptions
Depending on the resolution of the user's computer, the game will have to scale
its graphics to fit the screen. If there is an error in scaling, the size and 
position of in-game objects may become inconsistent between resolutions. For 
this reason the game should be tested on a selection of common resolutions to 
ensure this does not occur.

Invalid Inputs
Whilst the user controls their character via keyboard input it is possible they
may press the wrong keys. Whilst the game itself should not behave poorly even
when an invalid key is pressed, some operating systems such as Ubuntu and
Windows may change focus from the game's window, disrupting the user's session.

Unknown Inputs
Upon the first use of the game, a user may not know which inputs correspond to
which actions in the game. If this information is not made available to the user
anywhere in the game, the user may learn the correct inputs by trial and error,
or become frustrated and quit. Therefore the inputs should be made available to
the player before they play for the first time.
