% Chapter 1	System Overview
The artificial intelligent software which we are working on comes in
the form of a game. Our game will be developed using the language,
Python 3.5. This system may be used as a way to improve one’s
cognitive and motor skills or it may be used as a way to relieve
stress or even just to provide enjoyment.

This game will work in improving ones cognitive and motor skills
through requiring the individual to focus on the different colors of
the enemy ships which will only take damage should the individual
also be quick to choose the correct color prior to initiating an
attack. This process will help the player to improve their focus as
they are required to pay attention to the colors of each enemy ship,
improve their reaction time by forcing the player to think quickly
in which is the appropriate color to provide damage, and therefore
improve their overall decision making skills. The game will help to
relieve stress in the sense that the player will have the chance to
focus any aggressive feelings on the enemy ships within the game and
will provide satisfaction every time the player gets a hit and takes
down an enemy ship. Another way which this game will provide stress
relief and possibly even pain relief is through taking the players
focus off of whatever it is that is bothering them and placing that
focus on decisions required in order to win the game.

This product will require that the individual’s computer be able to
support Python 3.5 and may require the installation of the software,
Pygame, in order to run the product. Without these requirements in
place there is no guarantee that this game will run on the users’
device due to the build of the game.
