\documentclass[letterpaper,12pt]{article}
% \documentclass[12pt,twocolumn]{article}  % For once we have more than an abstract

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{natbib}
\usepackage[colorlinks=true]{hyperref}
\setkeys{Gin}{width=\linewidth}
\usepackage[margin=1.0in]{geometry}

\author{
    Reilly, Terrence\
    \and
    Justice, James\
    \and
    Goodall, Brad\
    \and
    Maresh, Keefer\
    \and
    Gleason, Meagon\
}
\title{Improving User Engagement to Arcade Style Shooters through Color Matching}
%\course{CPS410}

\begin{document}
% 1.   Title and authors
    \maketitle
    \linespread{1.5}
    \nocite{*}
    \begin{abstract}
        % (1)	First paragraph:
        % Describe why you have chosen this research project/topic (your motivation for
        % choosing this topic).
        Arcade style shooters enjoyed popularity throughout the 1980s and 1990s.
        Color and pattern matching games such as Simon, Bop-It, and Twister were
        also popular during this time.  While the popularity of both genres may
        have waned in recent years, the purchasing power and free time of the children
        who grew up in these decades has increased dramatically.  Few video
        games have tried to capitalize on the combined potential of these genres.

        % (2)	Second paragraph:
        % Describe what you are going to do for your proposed project to make
        % it different from the existing projects.
        % Read the sample abstract and learn from it.
        In this paper, we present a coherent schema for combining aspects of
        pattern-matching and arcade style shooters from the late 1980s and
        early 1990s.  Arcade replicas, and color matching games from this era
        are plentiful, but most games which amalgamate the two concepts are based on
        rhythm and music (e.g. Rock Band, Frets on Fire, etc.) We further assess
        the balance of game difficulty necessary to maintain user engagement.  We
        report qualitative results of players using a purpose-built color matching
        arcade style shooters built in Python.  Research was completed using small
        focus groups.

        % (3)	Third paragraph:
        % Describe the result of your research project.
        % Read the sample abstract and learn from it.
        Our results demonstrate that an engaging arcade-style experience is possible
        when combined with basic color matching. However, we present evidence
        suggesting that the action in such a game must be well-balanced to avoid
        becoming overly-difficult.
    \end{abstract}

    \bibliographystyle{apalike}
    \bibliography{rp1}
\end{document}
